---
title: "Lab 09 - Grading the professor, Pt. 1"
author: "Steph Bossert"
date: "5 april 2021"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
library(ggplot2)
?evals
view(evals)
```

### Exercise 1
Positively skewed, mean = 4.18, max = 5, 
Students tend to give positive evaluations for their professors as the data is positively skewed.


```{r score}
evals2 <- ggplot(evals, aes(x = score))
evals2 + geom_histogram(bins = 30, color = "white", fill = "blue") +
  geom_vline(aes(xintercept = mean(score)), 
             linetype = "dashed", size = 0.6)
summary(evals$score)

```

### Exercise 2
There is a direct, positive relationship between a professor's beuty score and their evalution score... interesting. 
```{r score and bty_avg}
ggplot(evals, aes(x=score, y=bty_avg)) + 
  geom_point(shape=18, color="blue")+
  geom_smooth(method=lm, se=FALSE, linetype="solid",
             color="red")

```
###Exercise 3
Jitter handles the overplotting of data, adds random variation 
```{r jitter}
ggplot(evals, aes(x=score, y=bty_avg)) + 
  geom_point(shape=18, color="blue")+
  geom_jitter()

ggplot(evals, aes(x=score, y=bty_avg)) + 
  geom_point(shape=18, color="blue")+
  geom_jitter(aes(colour = gender))

```
### Exercise 4
score = 3.88 + .07(bty_avg)
```{r regression}
m_bty = lm(score~bty_avg, data = evals) #Create the linear regression
summary(m_bty)
ggplot(evals, aes(x=score, y=bty_avg)) + 
  geom_point(shape=18, color="blue")+
  geom_smooth(method=lm, se=FALSE, linetype="solid",
             color="orange") +
  geom_jitter(aes(colour = gender))

```
###Exercise 5
```{r}
m_bty = lm(score~bty_avg, data = evals)
ggplot(evals, aes(x=score, y=bty_avg)) + 
  geom_point(shape=18, color="blue")+
  geom_smooth(method=lm, se=FALSE, linetype="solid",
             color="yellow") +
  geom_jitter() 
 
```
###Exercise 6
Slope = .07, small but direction associated between average beauty score and score

###Exercise 7
It's positive and fairly large, which makes sense given the positive skew of the distribution of scores

###Exercise 8
R squared = 0.04, so beauty rating accounts for 4% of the variance in average professor evaluation score. 

###Exercise 9/10
```{r new regression}
m_gen = lm(score~gender, data = evals) #Create the linear regression
summary(m_gen)
###y= .14(x) + 4.09
###males: .14(0) + 4/09
###females: y= .141(1) + 4.09
```


###Exercise 11
```{r another regression}
m_rank = lm(score~rank, data = evals) #Create the linear regression
summary(m_rank)
###y= 4.28 -.13(X1) + -.15(X2)
###interpret: zero on both scores means a score of 4.28, controlling for rank tenure track, a decrease in -.14 for the rank tenure position 
```


####Exercise 12 & 13
```{r ranke_level}
rank_evals <- evals%>%
  mutate(rank_relevel = case_when(rank== "tenure track" ~ 0,
                          rank== "teaching" ~ 1,
                          rank== "tenured" ~ 2))
m_rank_relevel<- lm( score~ rank_relevel, data = rank_evals) #Create the linear regression
summary(m_rank_relevel)
```
###13 Model: Y = 4.20 - .02(X)
A teacher who is on the tenure track has a rank of 4.20, then a teacher who is "teaching" decreases by -.02 and then a teacher who is tenured decreases by -.04
R square = .001

###Exercise 14
```{r tenure1}
tenure_eligible_evals<- evals%>% 
  mutate(Tenure_eligible = if_else(rank == "teaching", "No", "Yes"))
```

###Exercise 15
```{r tenure2}
m_tenure_eligible= lm( score~ Tenure_eligible, data = tenure_eligible_evals) #Create the linear regression
summary(m_tenure_eligible)
```
### Y = 4.28 -1.4(X)
###for teachers who are not tenure eligible: Y= 4.28 -(1.4)(0) , their score = 4.28, for those that are- Y= 4.28 -(1.4)(1)
###R square = .0015
